A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-11 manuscript.Rmd
work on simulation; unfinished!

```{r}
fit <-
  lavaan::cfa(
    model,
    data = simulated,
    group = "group",
    meanstructure = TRUE,
    std.lv = TRUE,
    group.equal = c("intercepts", "loadings")
  ) 
```

>>>>

Note, that this certainly results in different numbers each time we run it.
To consistently get the same results it is good practice to use a seed.
The function `seeded_generate()` will always generate the same pseudo-random numbers, when given the same seed.

```{r}
seeded_generate <-  function(seed, ...)withr::with_seed(seed, generate(...))
simulated <- seeded_generate(
  seed = 1234,
  n = 100000,
  diff = 0.1,
  vary_intercepts = rep(0.3, 3),
  vary_loadings = rep(0.3, 3),
  skewness = rep(5,-0.5)
)
```

```{r}
lavaan::summary(analyze(simulated))
```
